### 2022-02-10 abstract.tex
more tweaks

\begin{abstract}
    \acfp*{NCS} have long been a subject of theoretical research, however, little work has been devoted to repeatable and scalable experimentation.
    The advent of edge computing and the subsequent proliferation of \acsp*{NCS} has quickly led this to become a key issue that needs to be addressed.

    In this work, we present a novel, completely software-based approach to this challenge.
    Our core idea rests on a framework for the emulation of physical plants which communicate with controllers implemented in software over a real network.
    This approach is furthermore designed and built for the Edge, using a general-purpose programming language and with full compatibility with industry-standard containerization solutions.
    We validate this framework using an initial implementation of an inverted pendulum \acs*{NCS}.
    Our results showcase the utility of the tool as a repeatable, extensible, and scalable solution to \acs*{NCS} performance evaluation.
\end{abstract}

>>>>

\begin{abstract}
    In this work, we present \acs*{CLEAVE}, a novel, completely software-based framework for repeatable and scalable experimentation in \acfp*{NCS}.
    While these systems have long been a subject of both theoretical and experimental research, their inter-domain nature  has led to a wide number of task-specific approaches to research, and little work has been devoted to generalizable, repeatable, and scalable experimentation.
    We aim to tackle this gap in knowledge through an approach based on the emulation of physical plants which communicate over a real network with controllers implemented in software.
    \acs*{CLEAVE} is furthermore designed and built for the edge, using Python3 and with full compatibility with industry-standard containerization solutions.
    Although designed for single-loop emulations, the flexibility afforded by the aformentioned characteristics allow our framework to be adaptated to and employed in a multitude of more complex scenarios.

    We validate \acs*{CLEAVE} using an initial implementation of an inverted pendulum \acs*{NCS}.
    Our results showcase the utility of the tool as a repeatable, extensible, and scalable solution to \acs*{NCS} performance evaluation.
\end{abstract}

### 2022-02-10 intro.tex
more tweaks

Our framework, \ac{CLEAVE}, aims to simplify the repeatable and scalable benchmarking of such systems.
Our approach is fully virtualized, inspired by our previous work on benchmarking human-in-the-loop applications on the edge~\cite{Olguin2019EdgeDroid}.
We provide a benchmarking framework and software development kit for the development of emulated physical systems and softwarized controllers.
These virtual \acp{NCS} can then be deployed on real networks for reparametrizable, repeatable, and reproducible benchmarking of the complete system.

\ac{CLEAVE} is built using \emph{Python 3.8}, making it highly extensible and able to harness the hundreds-of-thousands of already existing user-provided libraries.
It is furthermore compatible with container technologies such as \emph{Docker}\footnote{Docker Engine: \url{https://www.docker.com/}}, making it suitable for automated deployment and benchmarking on industry-standard edge setups using container orchestration solutions.

>>>>

Our framework, \ac{CLEAVE}, aims to simplify the repeatable and scalable benchmarking of such systems.
\ac{CLEAVE} is fully virtualized, inspired by our previous work on benchmarking human-in-the-loop applications on the edge~\cite{Olguin2019EdgeDroid}.
The tool consists of a benchmarking framework and software development kit for the development of emulated physical systems and softwarized controllers.
These virtual \acp{NCS} can then be deployed on real networks for reparametrizable, repeatable, and reproducible benchmarking of the complete system.

\ac{CLEAVE} is built using \emph{Python 3.8}, making it highly extensible and able to harness the hundreds-of-thousands of already existing user-provided libraries.
It is furthermore compatible with container technologies such as \emph{Docker}\footnote{Docker Engine: \url{https://www.docker.com/}}, making it suitable for automated deployment, scaling, and benchmarking on industry-standard edge setups using container orchestration solutions.
